A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 main.tex
change 50136 to \[\]$

\subsubsection{Survival Time}
\label{accelerated}
By using adversarial samples (see Equation~\ref{eq:adv_success}), failures can be induced. The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$, since adversarial noise is known to \textit{induce} failures.
That is, the rate of adversarial success (Equation~\ref{eq:adv_success}), will increase as $\varepsilon$ increases.
In terms of AFT models, this can be expressed as the expected lifetime of an adversarial sample when treating $\varepsilon$ as a covariate.
In the language of accelerated failure time models, this can be expressed in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right),
\end{equation}
where $\phi_\theta$ is the acceleration factor, described by the joint effect of the covariates, such that
$$
    \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
$$
and where $x=(x_0, \ldots, x_n)$ is a vector of covariates and $\theta=(\theta_0, \ldots, \theta_n)$ describe the fitted parameters, and  $\varepsilon$ is used as one of the covariates. That is, when the adversarial noise level changes, it will also alter the expected survival time of a sample.
This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
However, in order to find the best AFT model, one must compare the tested models using the techniques outlined below.

>>>>

\subsubsection{Survival Time}
\label{accelerated}
By using adversarial samples (see Equation~\ref{eq:adv_success}), failures can be induced. The likelihood of that failure is dependent on the amount of adversarial noise, $\varepsilon$, since adversarial noise is known to \textit{induce} failures.
That is, the rate of adversarial success (Equation~\ref{eq:adv_success}), will increase as $\varepsilon$ increases.
In terms of AFT models, this can be expressed as the expected lifetime of an adversarial sample when treating $\varepsilon$ as a covariate.
In the language of accelerated failure time models, this can be expressed in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right),
\end{equation}
where $\phi_\theta$ is the acceleration factor, described by the joint effect of the covariates, such that
\[
    \phi_{\theta}(x) = \exp{ \left( \theta_{0} x_{0} + \theta_{1} x_{1} + \cdots + \theta_{n} x_{n} \right) },
\]
and where $x=(x_0, \ldots, x_n)$ is a vector of covariates and $\theta=(\theta_0, \ldots, \theta_n)$ describe the fitted parameters, and  $\varepsilon$ is used as one of the covariates. That is, when the adversarial noise level changes, it will also alter the expected survival time of a sample.
This assumption means we can evaluate the generalization performance using a small number of adversarial samples with our precision coming from careful time measurements rather than massive test sets~\cite{kleinbaum1996survival,meyers_aft}.
However, in order to find the best AFT model, one must compare the tested models using the techniques outlined below.
